---
title: "Analysis"
author: "Gordana Popovic"
date: "8 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```



To run analysis with alternate thresholds change below.
```{r}
rm(list=ls())
which_threshold=50  #threshold to use
source("soil_functions.R")

#define survival object for both full model and the sub models with just ref or undermined
if(which_threshold==50){
  f_surv=Surv(soil_narrow$days.above.50pcSM+1, soil_narrow$da50C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.50pcSM+1, da50C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.50pcSM+1, da50C))
}else if(which_threshold==25){
  f_surv=Surv(soil_narrow$days.above.25pcSM+1, soil_narrow$da25C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.25pcSM+1, da25C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.25pcSM+1, da25C))
}else if(which_threshold==75){
  f_surv=Surv(soil_narrow$days.above.75pcSM+1, soil_narrow$da75C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.75pcSM+1, da75C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.75pcSM+1, da75C))
}

```


### Does soil moisture persistence change with impact and veg type?

Here we fit the model to our data, with all the predictors we think might have an effect. `frailty` is what they call random effects in the survival literature.

```{r}

mod_aft=survreg(f_surv~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type_+Impact_+veg_type_Impact_+frailty(re),
               dist='weibull',data=soil_narrow)
anova(mod_aft)
```

The relevant p-values are next to veg_type, Impact and the interaction. Chi=square values are found by calculating differences in -2*LL.


#### Plots

```{r}
ndX=model.matrix(~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type*Impact,data=nd)
```

<!-- From https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html -->
```{r echo=FALSE, fig.height=3, fig.width=6, message=FALSE, warning=FALSE}
nd$log_pred=ndX%*%matrix(mod_aft$coefficients)
#plotting
#extract the variance-covariance matrix of the parameters V
Vb=mod_aft$var[1:ncol(ndX),1:ncol(ndX)]
#compute XVX' to get the variance-covariance matrix of the predictions;
#extract the diagonal of this matrix to get variances of predictions;
#take the square-root of the variances to get the standard deviations (errors) of the predictions;
Sp=sqrt(diag(ndX%*%Vb%*%t(ndX)))

#define lower and upper bounds
nd$log_lower=nd$log_pred-1*Sp
nd$log_upper=nd$log_pred+1*Sp

#days vector to predict
x=seq(0.001,55,length.out = 1000)

#mean and upper and lower bounds for plot
a <- 1/mod_aft$scale      
nd$b <- exp( nd$log_pred ) 
nd$lower=exp(nd$log_lower)
nd$upper=exp(nd$log_upper)


pred=tibble()
#predict persistence probability
for(i in 1:nrow(nd)){
  y <- 1-pweibull(x, shape=a, scale=nd$b[i])
  upper=1-pweibull(x, shape=a, scale=nd$upper[i])
  lower=1-pweibull(x, shape=a, scale=nd$lower[i])
  pred=rbind(pred,data.frame(x=x,y=y,upper=upper,lower=lower,veg_type=nd$veg_type[i],Impact=nd$Impact[i] ))
}

pred$Impact=factor(pred$Impact,levels=levels(pred$Impact),labels=c("Unmined","Mined"))
pred$veg_type=factor(pred$veg_type,levels=c("ttt","ch","wh","bt"),labels = c("Ti-tree thicket", "Cyperoid heath","Restioid heath / Sedgeland","Banksia thicket"))
```

```{r fig.height=4, fig.width=8}

ggplot(pred,aes(x, y,color =Impact, fill=Impact)) +  
  geom_ribbon(aes(ymin = lower, ymax = upper),linetype=2, alpha=0.1,data=pred) +
  facet_grid(~veg_type)+labs(y="Probability of persistence",x="Days")+theme_light()+
  scale_fill_manual(values=c("blue", "#E69F00"))+
  scale_color_manual(values=c("blue", "#E69F00"))+
  geom_line(size=1.1)+theme_classic()+
  theme(strip.background = element_blank(),legend.title=element_blank(),legend.position = "bottom")
```


#### Confidence intervals
```{r}
mat_out=my_ci_survreg(mod_aft,ndX)
mat_out$veg_type=nd$veg_type
mat_out$Impact=nd$Impact
mat_out[,c(20,21,17:19)]
```


### Do veg types differ for mined and unmined sites separately?


```{r}
mod_aft_Ref=survreg(f_surv_Ref~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type+frailty(re),
               dist='weibull',data=R_subdat)
wr=confint(mod_aft_Ref,level = 0.9)[10,]
anova(mod_aft_Ref)


```

Relevant p-value next to veg_type.

```{r}
mod_aft_Imp=survreg(f_surv_Imp~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type+frailty(re),
               dist='weibull',data=U_subdat)
wi=confint(mod_aft_Imp,level = 0.9)[10,]

anova(mod_aft_Imp)

```

Relevant p-value next to veg_type.

### Does persistence change over time, does this change differ between mined and unmined sites?


```{r}


soil_narrow$date=as.Date(soil_narrow$date,format="%d/%m/%Y")
soil_narrow$date_mined=as.Date(median(soil_narrow$date),format="%d/%m/%Y")


soil_narrow$days_since=as.numeric(soil_narrow$date-soil_narrow$date_mined)
soil_narrow$years_since=soil_narrow$days_since/365

A=model.matrix(~veg_type*Impact +years_since*Impact,data=soil_narrow)[,-1]
veg_type_=A[,1:3]
Impact_=A[,4]
years_since_=A[,5]
veg_type_Impact_=A[,6:8]
years_since_Impact_=A[,9]

soil_narrow[,11:17]=apply(soil_narrow[,11:17],2,scale)


f_surv_U <- with(soil_narrow,Surv(days.above.50pcSM+1, da50C))
mod_aft_time=survreg(f_surv_U~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type_+Impact_+veg_type_Impact_+years_since_+years_since_Impact_+frailty(re),
               dist='weibull',data=soil_narrow)

```


```{r}
anova(mod_aft_time)
```

```{r}
summary(mod_aft_time)
```
Relevant p-value next to years_since and years_since_Impact.

Calculate rate of reduction.
```{r}
1-exp(-0.000336-0.238997)
```

