---
title: "Supplementary analyses"
author: "Gordana Popovic"
date: "8 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```




```{r}
rm(list=ls())
which_threshold=50
library(coxme)
source("soil_functions.R")

#define survival object for both full model and the sub models with just ref or undermined
if(which_threshold==50){
  f_surv=Surv(soil_narrow$days.above.50pcSM+1, soil_narrow$da50C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.50pcSM+1, da50C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.50pcSM+1, da50C))
}else if(which_threshold==25){
  f_surv=Surv(soil_narrow$days.above.25pcSM+1, soil_narrow$da25C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.25pcSM+1, da25C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.25pcSM+1, da25C))
}else if(which_threshold==75){
  f_surv=Surv(soil_narrow$days.above.75pcSM+1, soil_narrow$da75C)
  f_surv_Imp <- with(U_subdat,Surv(days.above.75pcSM+1, da75C))
  f_surv_Ref<- with(R_subdat,Surv(days.above.75pcSM+1, da75C))
}

```

### Does soil moisture persistence change with impact and veg type?


```{r}
mod_cox <- coxme(f_surv ~ lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type*Impact + (1 | Swamp/Probe_no), soil_narrow)
anova(mod_cox)
```


## Cox model
### Do veg types differ for mined and unmined sites separately?


```{r}

mod_cox_Ref <- coxme(f_surv_Ref ~ lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type + (1 | Swamp/Probe_no), R_subdat)
anova(mod_cox_Ref)



```




```{r}

U_subdat$scarpdist=scale(U_subdat$scarpdist)
mod_cox_Imp <- coxme(f_surv_Imp ~ lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type + (1 | Swamp/Probe_no), U_subdat)
anova(mod_cox_Imp)

```

## AFT model with random effects for Swamp instead of probe.

### Does soil moisture persistence change with impact and veg type?



```{r}

mod_aft=survreg(f_surv~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type_+Impact_+veg_type_Impact_+frailty(Swamp),
               dist='weibull',data=soil_narrow)
anova(mod_aft)
```



### Do veg types differ for mined and unmined sites separately?


```{r}
mod_aft_Ref=survreg(f_surv_Ref~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type+frailty(Swamp),
               dist='weibull',data=R_subdat)
wr=confint(mod_aft_Ref,level = 0.9)[10,]
anova(mod_aft_Ref)


```




```{r}
mod_aft_Imp=survreg(f_surv_Imp~lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type+frailty(Swamp),
               dist='weibull',data=U_subdat)
wi=confint(mod_aft_Imp,level = 0.9)[10,]

anova(mod_aft_Imp)

```


##  frailtypack

```{r}
library(frailtypack)
modClu <- frailtyPenal(f_surv~
cluster(Swamp)+subcluster(re)+lsoil_moist_day_before+ltotal.rain.volume+laverage.days.no.rain+
                  scarpdist +temp+precip+area_ratio+Probe_depth+
                  veg_type + Impact,
data=soil_narrow,n.knots=8,kappa=c(50000),cross.validation = TRUE)


summary(modClu)
```

Attempt to use frailtypack resulted in results with confidence intervals that were much too narrow to be trusted.


## Different soil moisture cut-off (25% and 75%)

These can be recreated with the main analysis code by changing the cut-off value in the top of the code.











